Assessing the Accessibility of Protein Tunnels using Motion Planning

### 2017-09-10 paper.tex
last par. in intro to experiments shorten

Two motion planners were utilized: the proposed planner (described in Alg.~\ref{alg::main} and Alg.~\ref{alg::expand}), denoted as \RA\ in the rest of the paper, and the Retraction-based RRT~\cite{zhangRetraction}, denoted as \RB\ in the rest of the paper.
The \RA\ method was run with the following parameters:
$\Imax=5,000$, $m=100$, $\gb=0.9$, $\dt=1.5$~\AA, $\rv=2$~\AA\ and $\varepsilon=0.05$~\AA.
Both methods were implemented in the same software framework and they utilized the same data structures and routines for the collision detection and nearest-neighbor search.
The nearest-neighbor search of both planners was based on the 6D Euclidean metric with the same weights for rotation and translation parts.
This metric was selected based on preliminary experiments with both planners as it resulted in the success rates.

@@

In the following experiments, we measured the performance of the methods using the traversability rate, which is the percentage of frames of the protein dynamics that are traversable by the tested ligand.
A frame is considered traversable if at least one trajectory out of 20 (the number of initial configurations $|\QI|$) $\times$ 10 trials approaches the active site to the distance less than 2~\AA.~\footnote{We refer to~\url{http://mrs.felk.cvut.cz/icra2018protein} for additional material.}

@@

{\def\a{270}
\begin{figure}[hb]
\centering
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1rrt_path_time-2}
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1trajDistToGoal-2}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop1}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop2}
\caption{\label{fig::comparison}
    Runtimes and the distance to the active site for the m037 ligand at scale 0.6.
    The values are computed from all 200 trials (20 initial configurations $\times$ 10 trials).
    Only each second frame is shown in the graph.
}
\end{figure}
}

>>>>

Two motion planners were utilized: the proposed planner (described in Alg.~\ref{alg::main} and Alg.~\ref{alg::expand}), denoted as \RA\ in the rest of the paper, and the Retraction-based RRT~\cite{zhangRetraction}, denoted as \RB\ in the rest of the paper.
The \RA\ method was run with the following parameters:
$\Imax=5,000$, $m=100$, $\gb=0.9$, $\dt=1.5$~\AA, $\rv=2$~\AA\ and $\varepsilon=0.05$~\AA.
Both methods were implemented in the same software framework and they utilized the same data structures and routines for the collision detection and nearest-neighbor search.
The nearest-neighbor search of both planners was based on the 6D Euclidean metric with the same weights for rotation and translation parts.
This metric was selected based on preliminary experiments with both planners as it resulted in the highest success rates.

@@

In the following experiments, we measured the performance of the methods using the traversability rate, which is the percentage of frames of the protein dynamics that are traversable by the tested ligand.
A frame is considered traversable if at least one trajectory out of 200 ($\!|\QI|\!\times\!\!10$ trials) approaches the active site to the distance less than~2~\AA.~\footnote{We refer to~\url{http://mrs.felk.cvut.cz/icra2018protein} for additional material.}

@@

{\def\a{270}
\begin{figure}[hb]
\centering
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1rrt_path_time-2}
%\includegraphics[width=0.17\textwidth,angle=\a]{fig/m037tmins-03tunnel-1trajDistToGoal-2}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop1}
\includegraphics[width=0.18\textwidth,angle=\a]{fig/crop2}
\caption{\label{fig::comparison}
    Runtimes and the distance to the active site for the m037 ligand at scale 0.6.
    The values are computed from all 200 trials (20 initial configurations $\times$ 10 trials).
    Only each third frame is shown in the graph.
}
\end{figure}
}
